An Embedding Framework for Consistent Polyhedral Surrogates

### 2021-04-23 poly-embed-journal/poly-embed-journal.tex
Re-org Section 5 with TFAE

\begin{definition}[Non-redundancy]\label{def:nonredundant}
	A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
	A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
\end{definition}

\begin{definition}[Tight embedding]\label{def:tight-embedding}
	We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\R$ is non-redundant.
\end{definition}

\begin{definition}[Trim]\label{def:trim}
	Given an elicitable property $\Gamma:\simplex \toto\R$, we define $\trim(\Gamma) = \{\Gamma_u : u \in \R \text{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$ as the set of maximal level sets of $\Gamma$.
\end{definition}

\begin{proposition}\label{prop:nonredundant-iff-trim}
	Suppose $L$ elicits $\Gamma$.
	If a  set $\R$ is non-redundant for $L$ then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
\end{proposition}
\begin{proof}
	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
	If $\R$ is non-redundant, then every $r \in \R$ uniquely optimizes $L$ for some $p_r \in \simplex$.
	First, we have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$ trivially.
	Consider $r \in \R$.
	Since there is a $p_r \in \simplex$ so that$\Gamma(p_r) = \{r\}$.
	Therefore, we cannot have $\Gamma_r \subseteq \Gamma_{r'}$ for any other $r' \neq r \in \R$, and therefore $\Gamma_r \in \trim(\Gamma)$.
\end{proof}

\begin{proposition}\label{prop:min-rep-iff-trim}
	Suppose $L$ elicits $\Gamma$.
	If a  set $\R$ is a finite minimum representative set then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
\end{proposition}
\begin{proof}
	\jessie{Not an iff because you can have duplicate reports, which is consolidated by trim}
\end{proof}

\begin{corollary}
	$\R$ is non-redundant for $L$ if and only if $\R$ is a minimum representative set for $L$.
\end{corollary}

\begin{corollary}
	If $\R$ is a minimum representative set for $\ell$ and $L$ embeds $\ell$ over $\R$, then $L$ tightly embeds $\ell$.
\end{corollary}

\jessie{TODO: Relate to trim}

@@

\begin{proposition}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \affhull(\simplex)$.
	\end{enumerate}
	%\raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}
	Let $L$ elicit $\Gamma$.

>>>>

\begin{definition}[Non-redundancy]\label{def:nonredundant}
A loss $L : \R \to \reals^\Y_+$ eliciting $\Gamma:\simplex \toto \R$ is \emph{redundant} if there are reports $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and \emph{non-redundant} otherwise.
\end{definition}

%\begin{definition}[Non-redundancy]\label{def:nonredundant}
%	A report $r \in \R$ is \emph{redundant} for the discrete loss $\ell : \R \to \reals_+^\Y$ if $r$ does not uniquely optimize $\inprod{p}{\ell(\cdot)}$ for any $p \in \simplex$.
%	A set $\R$ is called \emph{non-redundant} if it contains no redundant reports.
%\end{definition}

%commented out 23 Apr 21
%\begin{proposition}\label{prop:min-rep-implies-trim}
%	Suppose $L$ elicits $\Gamma$.
%	If the set $\R$ is a finite minimum representative set for $L$, then $\{\Gamma_r \mid r \in \R\} = \trim(\Gamma)$.
%\end{proposition}
%\begin{proof}
%We trivially have $\trim(\Gamma) \subseteq \{\Gamma_r \mid r \in \R\}$, so the other directino of inclusion is what's left to show.
%For $r \in \R$, we want to show $\Gamma_r \in \trim(\Gamma)$.
%
%\jessie{Implicit lemma about 3 ways to be redundant used here.}
%We proceed in three cases: if there is not an $r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, then $L$ is non-redundant.
%If there is an $r'$ such that $\Gamma_r = \Gamma_{r'}$, $\R$ being a minimum representative set implies $r = r'$.
%If there is an $r'$ such that $\Gamma_r \subsetneq \Gamma_{r'}$, then $\R \setminus \{r\}$ is also a representative set, so we contradict $\R$ being a minimum representative set.
%Therefore, $\Gamma_r \in \trim(\Gamma)$.
%\end{proof}
%
%\begin{proposition}
%	Let $L : \R' \to \reals^\Y_+$ be a given loss function and $\R$ a \jessie{finite?} representative set for $L$.
%	$L|_\R$ is non-redundant $\iff \R$ is a minimum representative set for $L$.
%\end{proposition}
%\begin{proof}
%	$\implies$ If $L|_\R$ is non-redundant, then for any $r \in \R$, we want to show there exists a $p \in \simplex$ such that $\Gamma(p) \cap \R \setminus \{r\} = \emptyset$.
%	By non-redundancy, we know there is no $r'$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
%	Therefore, if $r' \in \Gamma(p) \cap \R \setminus \{r\}$, we must still have some $p' \in \simplex$ so that $r' \not \in \Gamma(p')$.
%	In particular, we claim that $\Gamma(p') \cap \R \setminus \{r\} = \emptyset$. \jessie{Prove this claim!}
%	
%	$\impliedby$
%	We show the contrapositive: if $L|_\R$ is redundant, then $\R$ is not a minimum representative set for $L$.
%	In particular, there is a pair, $r, r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$, and we can thus verify $\Gamma(p) \cap \R \setminus \{r\}$ is also a representative set.
%	Therefore, $\R$ is not a minimum representative set.
%\end{proof}

\begin{proposition}\label{prop:tfae-min-rep-nonredundant}
	Let $\R$ be a finite representative set for $L$ eliciting $\Gamma$.
	The following are equivalent:
	\begin{enumerate}
		\item[a.] $\R$ is a minimum representative set for $L$.
		\item[b.] $L|_\R$ is non-redundant.
		\item[c.] For all $r \in \R$, $\Gamma_r$ is full-dimensional, the multiset $\{\Gamma_r : r \in \R\}$ has no duplicate elements, and $\cup_{r\in\R} \Gamma_r = \simplex$.
	\end{enumerate}
\end{proposition}
\begin{proof}[Sketch]
	$(a \implies b)$  
	We show the contrapositive: suppose $L|_\R$ is redundant.
	Then there is a $r,r' \in \R$ such that $\Gamma_r \subseteq \Gamma_{r'}$.
	Then for all $p \in \Gamma_r$, we have $\{r, r'\} \subseteq \Gamma(p)$.
	Therefore, $\R \setminus \{r\}$ still a representative set, so $\R$ is not minimum.

	$(b \implies c)$
	If $L|_\R$ is non-redundant, then for all $r \in \R$, there is no $r'$ so that $\Gamma_r \subseteq \Gamma_{r'}$.
	This means the multiset $\{\Gamma_r : r \in \R\}$ contains no duplicate elements, since it has duplicate elements if and only if $\Gamma_r = \Gamma_{r'}$.
	Moreover, each $\Gamma_r$ is full-dimensional, since if there was a $\Gamma_r$ that was lower dimensional, it would have to be a subset of another level set, which would contradict non-redundancy. \jessiet{Hand waving here}
	Finally, we have $\cup_{r \in \R} \Gamma_r = \simplex$ since $\R$ is representative.

	$(c \implies a)$
	As $\Gamma_r$ is full-dimensional and the multiset $\{\Gamma_r : r \in \R\}$ contains no duplicate elements (that is, there are no $r, r' \in \R$ such that $\Gamma_r = \Gamma_{r'}$), for each $r \in \R$ there must be some distribution $p_r \in \simplex$ so that $\Gamma(p_r) = \{r\}$.
	Thus, $\R \setminus \{r\}$ not a representative set for all $r \in \R$.
	Therefore, $\R$ is minimum.
\end{proof}

\begin{definition}[Tight embedding]\label{def:tight-embedding}
	We say that a loss $L : \reals^d \to \reals_+^\Y$ \emph{tightly embeds} a discrete loss $\ell : \R \to \reals_+^\Y$ via the injection $\varphi :\R \to \reals^d$ if $L$ embeds $\ell$ and $\ell$ is non-redundant.
\end{definition}

\begin{corollary}
	If $\R$ is a minimum representative set for $L$ eliciting $\Gamma$, then $L$ tightly embeds $L|_\R$.
\end{corollary}

\begin{definition}[Trim]\label{def:trim-loss}
	Given an loss $L : \R \to \reals^\Y_+$, we define $\trim(L) = \{L(u) : u \in \R \textrm{ s.t. } \neg\exists u'\in\R,u'\neq u,\, \Gamma_u \subsetneq \Gamma_{u'}\}$.
\end{definition}

Observe that if a loss $L : \R \to \reals_+^\Y$ is non-redundant, then $\{L(r) \mid r \in \R\} = \trim(L)$ by applying the definition of non-redundancy.

\begin{corollary}
	$\trim(L)$ is unique.
\end{corollary}
This follows from Proposition~\ref{prop:tfae-min-rep-nonredundant}, as $\trim(L)$ moves from $L$ to remove any non-redundant reports.
$\trim$ removes redundancy of strict subsets (that is, $\Gamma_r \subseteq \Gamma_{r'}$) by the set comprehension, while it removes fully redundant losses ($\Gamma_r = \Gamma_{r'}$) by definition of a set.

\begin{proposition}
	Let $\ell$ be a discrete loss.
	$L$ embeds $\ell$ if and only if $\trim(L) = \trim(\ell)$.
\end{proposition}

@@

\begin{proposition}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
	\end{enumerate}
	%\raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}
	Let $L$ elicit $\Gamma$.
